### 2018-03-06 analysis_code/agents_table.Rmd
commit a bunch of results + some tweaks to analysis scripts

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_raw_results_4.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
EXPERIMENT_1_CV_HIGH <- 156.71410383 #chisquared critical values for 124 degrees of freedom
EXPERIMENT_1_CV_LOW <- 95.07008897

EXPERIMENT_2_CV_HIGH <- 128.42198864
EXPERIMENT_2_CV_LOW <- 73.36108019

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy")
print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (prior in priors) {
  for (j in 1:length(time_horizons)) {
    results <- matrix(nrow=length(agent_algs), ncol=length(algs))
    colnames(results) <- c(paste(concise_alg_rep(alg_pairs[1]), concise_alg_rep(alg_pairs[2]), sep=" vs "), paste(concise_alg_rep(alg_pairs[3]), concise_alg_rep(alg_pairs[4]), sep=" vs "), paste(concise_alg_rep(alg_pairs[5]), concise_alg_rep(alg_pairs[6]), sep=" vs "))
    rownames(results) <- get_agent_rep(agent_algs)
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=2)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=2)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=2)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares_percent, "%")
        }
      }
      tab <-xtable(results, caption=paste("Results for", time, prior))
      print(tab, type="html")
  }
  print('<br><br><br><br><br><br>')
  }

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000, 5000, 10000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy") #"ThompsonSampling", "ThompsonSampling", "DynamicEpsilonGreedy", "DynamicEpsilonGreedy", "DynamicGreedy", "DynamicGreedy")
#print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
#print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (memory in memory_sizes) {
for (prior in priors) {
    for (j in 1:length(time_horizons)) {
      results <- matrix(nrow=length(agent_algs), ncol=(length(alg_pairs) / 2))
    colnames(results) <- c(paste(concise_alg_rep(alg_pairs[1]), concise_alg_rep(alg_pairs[2]), sep=" vs "), paste(concise_alg_rep(alg_pairs[3]), concise_alg_rep(alg_pairs[4]), sep=" vs "), paste(concise_alg_rep(alg_pairs[5]), concise_alg_rep(alg_pairs[6]), sep=" vs ")) #paste(concise_alg_rep(alg_pairs[7]), concise_alg_rep(alg_pairs[8]), sep=" vs "), paste(concise_alg_rep(alg_pairs[9]), concise_alg_rep(alg_pairs[10]), sep=" vs "), paste(concise_alg_rep(alg_pairs[11]), concise_alg_rep(alg_pairs[12]), sep=" vs "))
    rownames(results) <- get_agent_rep(agent_algs)
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == memory & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=1)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          cv_high <- qchisq(.975, df=length(share) - 1)
          cv_low <- qchisq(.025, df=length(share) - 1)
          lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=1)
          high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=1)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>Var:", signif(var(share), digits=2), "<br>", shares_percent, "%")
      }
    }
      tab <-xtable(results, caption=paste("Results for", "t=",time, prior, "Memory=", memory))
      print(tab, type="html")
  }
  }
}

### 2018-03-06 analysis_code/tournament_table.Rmd
commit a bunch of results + some tweaks to analysis scripts

@@

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
EXPERIMENT_1_CV_HIGH <- 156.71410383 #chisquared critical values for 124 degrees of freedom
EXPERIMENT_1_CV_LOW <- 95.07008897

EXPERIMENT_2_CV_HIGH <- 128.42198864
EXPERIMENT_2_CV_LOW <- 73.36108019

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (prior in priors) {
  for (i in 1:length(agent_algs)) {
    agent_alg <- agent_algs[i]
    for (j in 1:length(time_horizons)) {
      time <- time_horizons[j]
      results <- matrix(nrow=length(algs), ncol=length(algs))
      colnames(results) <- algs
      rownames(results) <- algs
      for (k in 1:length(algs)) {
        for (l in 1:length(algs)) {
          p1alg = algs[k]
          p2alg = algs[l]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=4)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=4)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=4)
          results[k, l] <- paste("<b>",signif(mean(share), digits=4), "</b> +/-", cin, "<br>", signif(var(share), digits=4), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares)
        }
      }
      tab <-xtable(results, caption=paste("Results for", agent_alg, time, prior))
      print(tab, type="html")
    }
    print('<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>')
  }
}

>>>>

 <style>
   th,td{
     padding:10px;
   }
 </style>

@@

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000, 10000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- algs
        rownames(results) <- algs
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares)
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }
